An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-22 scagnostics.Rmd
Added mean and connecting line to timing plot.

@@

#timerMelt <- melt(dfTimer, id="n")
ggplot(dfTimer, aes(x = n, y = t, color=name)) + 
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Sample Size", y = "Time [s]", color = "Index family")
```

>>>>

\textcolor{red}{The plot is not perfect. I use alpha to fade out points, but cant find value that gives nice picture here. In addition the timer isnt precise enough to resolve timing for some indexes on small datasets, they are zeroes, appear on bottom of the log10 y axis.}

@@

timerMeans <- dfTimer %>%
  group_by(name, n) %>%
  summarise(t=mean(t))

ggplot(dfTimer, aes(x = n, y = t, color=name)) + 
  geom_point(alpha=0.05) +
  geom_point(data=timerMeans) +
  geom_line(data=timerMeans) +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Sample Size", y = "Time [s]", color = "Index family")
```
